\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-20 notes/2loopNLSM.tex
Lorenz gauge comment

We can achieve this construction by splitting the gauge group of the full Yang-Mills action from $G$ to $G_L \times G_R$, where the full non-abelian gauge symmetry is restored only when we identify $G_L = G_R$. However, if we break the left gauge group down to $G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to $G_R \rightarrow U(N)$, then we are left with a semi-abelian theory that is gauge invariant in the preferred $U(1)$-directions. We call this manifestly color-dual theory, \textit{semi-abelian Yang-Mills},
\begin{eBox}
\begin{equation}
\label{eq:semiYM}
\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
\end{equation}
\end{eBox}
where
\begin{equation}
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
\end{equation}
\begin{equation}
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c .
\end{equation}
Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents. Indeed, as we describe in Appendix \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{Cheung:2016prv}, J-theory \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills \cite{Monteiro2011pc}.
Specifically, semi-abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
The Feynman rule for the cubic vertex is
\begin{equation}
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3).
\end{equation}
The propagator kinetic mixes between the two gauge fields and has the standard Feynman rule of $i/k^2$.
We can use the Ward identity of \cref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant when the abelian polarizations are taken to be longitudinal, $\bar{\varepsilon} \rightarrow k$.

@@

\paragraph{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
The construction begins with a first order formulation of NLSM in terms of chiral currents $J^\mu$.
First order formulation of NLSM in terms of chiral current $J^\mu$.
Two equations.
Two constraints, the field strength should vanish
\begin{equation}
\label{eq:FieldStrengthJ}
F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
\end{equation}
which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
The second condition is that the chiral current should be in Lorenz gauge
\begin{equation}
\label{eq:LorenzGaugeJ}
\partial_\mu J^\mu=0
\end{equation}
which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
\begin{equation}
\label{eq:JTheoryEOM}
\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
\end{equation}
Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
In other words, \emph{J-theory and semi-abelian YM are identical}.
By calculating an off-shell 4-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
As might be expected, the kinematic algebra is the diffeomorphism algebra.
For details about external states and how to extract NLSM (a scalar theory) from semi-YM (a vector theory) we refer the reader to \cite{Cheung:2021zvb}.
Note that the different external particles break manifest Bose symmetry.

>>>>

We can achieve this construction by splitting the gauge group of the full Yang-Mills action from $G$ to $G_L \times G_R$, where the full non-abelian gauge symmetry is restored only when we identify $G_L = G_R$. However, if we break the left gauge group down to $G_L \rightarrow U(1)^{N^2}$ and take the right gauge group to $G_R \rightarrow U(N)$, then we are left with a semi-abelian theory that is gauge invariant in the preferred $U(1)$-directions. We call this manifestly color-dual theory, \textit{semi-abelian Yang-Mills},
\begin{eBox}
\begin{equation}
\label{eq:semiYM}
\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
\end{equation}
\end{eBox}
where
\begin{equation}
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
\end{equation}
\begin{equation}
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a + f^{abc} A_\mu^b A_\nu^c
\end{equation}
and $A_\mu$ is in Lorenz gauge.
Here we can think of the abelian vector as a background field that sources on-shell $A_\mu$ currents. Indeed, as we describe in Appendix \cref{sec:CKLagrangians}, semi-abelian Yang-Mills theory is at the heart of YZ-theory \cite{Cheung:2016prv}, J-theory \cite{Cheung:2020djz,Cheung:2021zvb}, and self-dual Yang-Mills \cite{Monteiro2011pc}.
Specifically, semi-abelian YM is simply a clever reinterpretation of the Lagrangian obtained by integrating an auxiliary field into the J-theory equations of motion.
The Feynman rule for the cubic vertex is
\begin{equation}
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3).
\end{equation}
The propagator kinetic mixes between the two gauge fields and has the standard Feynman rule of $i/k^2$.
We can use the Ward identity of \cref{eq:GIrelA} to check that the amplitudes are indeed gauge invariant when the abelian polarizations are taken to be longitudinal, $\bar{\varepsilon} \rightarrow k$.

@@

\paragraph{J-theory} There is an alternative color-dual formulation of NLSM that the theory manifestly corresponds to NLSM at least at tree level \cite{Cheung:2021zvb}.
For related formulations of NLSM that do not treat color-kinematics duality see \cite{Freedman:1980us, Slavnov:1971mz}.
The construction begins with a first order formulation of NLSM in terms of chiral currents $J^\mu$.
First order formulation of NLSM in terms of chiral current $J^\mu$.
Two equations.
Two constraints, the field strength should vanish
\begin{equation}
\label{eq:FieldStrengthJ}
F_{\mu\nu}(J) = \partial_\mu J_\nu - \partial_\nu J_\mu + g[J_\mu , J_\nu]=0
\end{equation}
which then implies that $J^\mu$ is pure gauge $J_\mu = U \partial_\mu U^{-1}$.
The second condition is that the chiral current should be in Lorenz gauge
\begin{equation}
\label{eq:LorenzGaugeJ}
\partial_\mu J^\mu=0
\end{equation}
which then yields the NLSM equation of motion $\partial_\mu (U \partial^\mu U^{-1})=0$.
Taking a linear combination of \cref{eq:FieldStrengthJ} and \cref{eq:LorenzGaugeJ} yields
\begin{equation}
\label{eq:JTheoryEOM}
\Box J^\mu +g f^{abc} J^\nu \partial_\nu J^\mu = 0.
\end{equation}
Integrating in an auxiliary field $\bar{J}^\mu$ as a Lagrange multiplier trivially produces the Lagrangian of semi-abelian YM \cref{eq:semiYM} but with the gauge fields renamed to $J_\mu$ and $\bar{J}_\mu$.
Since both theories are in Lorenz gauge this means that \emph{J-theory and semi-abelian YM are identical}.
By calculating an off-shell 4-point correlation function it is possible to check that this Lagrangian automatically satisfies color-kinematics duality.
As might be expected, the kinematic algebra is the diffeomorphism algebra.
For details about external states and how to extract NLSM (a scalar theory) from semi-YM (a vector theory) we refer the reader to \cite{Cheung:2021zvb}.
Note that the different external particles break manifest Bose symmetry.
